%% !TEX program = xelatex
\documentclass[11pt,a4paper]{article}

\usepackage[a4paper,margin=1.45cm]{geometry}
\usepackage{fontspec}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\IfFontExistsTF{TeX Gyre Heros}{
  \setmainfont{TeX Gyre Heros}
}{
  \setmainfont{Noto Sans}
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.2em}
\linespread{1.12}
\emergencystretch=1em
\setlist[itemize]{leftmargin=1.15em,itemsep=0.12em,topsep=0.12em}

\titleformat{\section}{\Large\bfseries}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{0.65em}{0.3em}

\newcommand{\project}[4]{
  \begin{samepage}
  \vspace{0.35em}
  \noindent
  \begin{tabular*}{\linewidth}{@{}p{0.72\linewidth}@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & \textit{#2} \\
  \end{tabular*}
  \textit{Stack: #3}
  \end{samepage}
  \begin{itemize}
    #4
  \end{itemize}
}

\newcommand{\skillentry}[5]{
  \item \textbf{#1} \\
  \textbf{Frameworks:} #2; #3 \\
  \textbf{Core technologies:} #4, #5
}

\begin{document}

{\LARGE \textbf{Tymur Kramar}} \\
Kosice, Slovakia \\
\href{mailto:tymur.kramar@gmail.com}{tymur.kramar@gmail.com} \,|\, +421 949 176 506 \,|\, \href{https://www.linkedin.com/in/tymur-kramar-3ab934268/}{linkedin.com/in/tymur-kramar-3ab934268}

\section*{Summary}
\begin{itemize}[itemsep=0.08em,topsep=0.08em]
  \item Backend developer with production experience in Go, Python, TypeScript, and Java.
  \item Built AI-enabled platforms: document ingestion pipelines, RAG/agent workflows, and domain-focused API services.
  \item Delivered cross-chain and trading infrastructure, including SDKs, indexers, and high-frequency market data collectors, with end-to-end ownership from architecture to production support.
  \item Strong with AI-assisted development tools and coding agents to accelerate repetitive engineering workflows while keeping architecture, implementation, and code quality under direct control.
\end{itemize}

\section*{Technical Matrix}
\begin{itemize}[itemsep=0.06em,topsep=0.06em]
  \skillentry
    {Go}
    {gRPC + grpc-gateway (protobuf-first)}
    {testing + testify (assert, require, mock)}
    {PostgreSQL (pgx), Cosmos SDK integrations, observability}
    {gRPC, REST}

  \skillentry
    {Python}
    {FastAPI}
    {pytest}
    {PostgreSQL (asyncpg, psycopg2), SQLAlchemy, Alembic, OpenAI Agent SDK}
    {REST, RPC}

  \skillentry
    {TypeScript}
    {Fastify (Node.js backend services)}
    {Jest}
    {Node.js, Zod, OpenAI APIs, gRPC/protobuf clients, blockchain SDKs}
    {REST, gRPC, WebSocket}

  \skillentry
    {Java}
    {Micronaut + GraalVM Native Image}
    {Spock}
    {PostgreSQL, Liquibase, Google Sheets API, OpenTelemetry}
    {REST}

  \skillentry
    {Linux and AWS}
    {Arch Linux (daily driver)}
    {Production operations, observability, reliability, bash scripting, systemd services, SSH/access security basics}
    {Docker, EC2, Lambda, S3, RDS, VPC, infrastructure provisioning}
    {HTTP/REST, gRPC}
\end{itemize}

\section*{Domain Focus}
\begin{itemize}[itemsep=0.08em,topsep=0.08em]
  \item AI-enabled backend systems: document ingestion pipelines, RAG/agent workflows, retrieval-oriented services.
  \item Blockchain and cross-chain infrastructure: SDKs, bridge integrations, and multi-hop transfer indexing.
  \item Trading systems: high-frequency market data collectors, execution services, and analytics APIs.
\end{itemize}

\section*{Languages}
\textbf{English:} Working proficiency \quad
\textbf{Slovak:} Basic comprehension \quad
\textbf{Russian:} Fluent \quad
\textbf{Ukrainian:} Native

\section*{Education}
\textbf{Technical University of Kosice (TUKE)} \hfill \textit{2023 -- Present} \\
Final academic year (in progress)

\newpage

\section*{Experience}
\textbf{Backend Developer} \hfill \textit{Jun 2024 -- Present} \\
\textit{Nitka, Remote (Full-time)}
\begin{itemize}
  \item Delivered backend systems for AI-assisted HR tools, agentic search platforms, cross-chain bridge infrastructure, and trading products.
  \item Owned full delivery cycle on several projects: architecture, implementation, data modeling, APIs, and maintenance.
  \item Worked deeply with PostgreSQL across all major projects.
  \item Most implementation details are intentionally limited due to NDA; projects were delivered for large, well-known client organizations.
\end{itemize}

\section*{Selected Projects at Nitka}
\project
  {AI HR Platform (resume/opening matching + Slack workflows)}
  {Jun 2024 -- Feb 2025}
  {Python, FastAPI, PostgreSQL, OpenAI API, Slack bot tooling, React, TypeScript}
  {
    \item Built backend flows to ingest resumes and job openings from PDF, Google Docs, and Microsoft document sources.
    \item Implemented AI-assisted candidate-to-opening scoring and ranking logic used by HR workflows.
    \item Enabled Slack-based usage where recruiters could submit resumes and retrieve top candidate matches from the internal database.
  }

\project
  {RAG + Agent Intelligence Platform}
  {Mar 2025 -- Jun 2025}
  {Python, FastAPI, PostgreSQL, SQLAlchemy, Alembic, OpenAI Agent SDK, TypeScript, React}
  {
    \item Designed and implemented the system end-to-end: nightly ingestion, parsing, chunking, vectorization, indexing, and API layer.
    \item Processed thousands of PDF files and tens of thousands of JSON records for searchable structured + unstructured intelligence.
    \item Implemented a tool-augmented agent (RAG + DB/search/API tools) that generated summaries, tables, and domain-focused chat answers.
  }

\project
  {AI Trading Agents Research (Osmosis)}
  {May 2025 -- Aug 2025}
  {TypeScript, OpenAI APIs}
  {
    \item Built and tested agent-based trading and pool-rebalancing strategies in a research environment.
    \item Implemented architecture and core logic solo, comparing AI-driven strategies against baseline automated bots.
  }

\project
  {Cross-Chain Bridge SDK (TypeScript) + Blockchain Integration}
  {Aug 2025 -- Dec 2025}
  {TypeScript, gRPC, protobuf, Cosmos SDK, Zod}
  {
    \item Designed and implemented a modular SDK for cross-chain transaction building and bridge interactions.
    \item Added support patterns for UTXO-like, EVM-like, TON, Solana, Ripple, and internal chain workflows.
    \item Delivered a production SDK used by frontend applications for cross-chain transfers.
  }

\project
  {Cross-Chain Indexer and High-Frequency Market Data Collectors}
  {Sep 2025 -- Dec 2025}
  {Go, PostgreSQL, gRPC/protobuf, scheduled jobs, observability}
  {
    \item Built and maintained services that tracked multi-hop bridge routes across dozens of chains.
    \item Implemented transfer indexing logic for complex hop scenarios (for example: Base -> Wormhole -> Solana -> internal chain -> BTC).
    \item Implemented high-frequency collectors for trading-related tick and execution data pipelines.
  }

\project
  {Backend Developer (project stream, Java) -- in parallel}
  {Sep 2025 -- Jan 2026}
  {Java, Micronaut, GraalVM Native Image, PostgreSQL, Liquibase, Google Sheets API, OpenTelemetry, Spock}
  {
    \item Worked as a core developer in a Java backend stream, contributing to key technical decisions with domain-heavy requirements.
    \item Built API services that ingested and transformed Google Sheets data and exposed stable contract-driven endpoints.
    \item Implemented instrumentation and test coverage for production reliability and operational visibility.
  }

\project
  {Multi-Chain Trading Engine}
  {Jan 2026 -- Present}
  {Go, PostgreSQL, internal trading APIs}
  {
    \item Contributing to a production trading backend for multi-chain and multi-exchange strategy execution.
    \item Delivering core API/features and performance improvements across trading and analytics components.
  }

\end{document}
